Covariate analysis of HBCC RNASeq data reprocessed with STAR-feature counts workflow with Ensembl v75 (DLPFC with CQN normlaisation)

### 2017-08-16 code/Rmd/HBCC_DLPFC_STAR_ENSEMBL_v75_CQN_qSVA.Rmd
Changed qSVA degration matrix id for HBCC

# Get quality surrogate variables
qSV_DEG_MAT_ID = 'syn10284941'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = qSV_DEG_MAT_ID
qSV_DEG_MAT = downloadFile(qSV_DEG_MAT_ID)
tmp = t(qSV_DEG_MAT[,-(1)])
colnames(tmp) = qSV_DEG_MAT$V1
qSV_DEG_MAT = tmp[,colnames(tmp) %in% colnames(COUNT)]
rownames(qSV_DEG_MAT) = rownames(tmp)
qSV = sva::qsva(qSV_DEG_MAT)
colnames(qSV) = paste0('qSV', 1:dim(qSV)[2])

>>>>

# Get quality surrogate variables
qSV_DEG_MAT_ID = 'syn10315615'
ALL_USED_IDs[length(ALL_USED_IDs)+1] = qSV_DEG_MAT_ID
qSV_DEG_MAT = downloadFile(qSV_DEG_MAT_ID)
tmp = t(qSV_DEG_MAT[,-(1)])
colnames(tmp) = qSV_DEG_MAT$V1
qSV_DEG_MAT = tmp[,colnames(tmp) %in% colnames(COUNT)]
rownames(qSV_DEG_MAT) = rownames(tmp)
qSV = sva::qsva(qSV_DEG_MAT)
colnames(qSV) = paste0('qSV', 1:dim(qSV)[2])
